### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/060_employement_city_thresh.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:25:09
\begin{table}[!htbp] \centering 
  \caption{Deciles Employment} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.750$^{**}$ & 0.079 & $-$1.013$^{***}$ & 2.539$^{*}$ & 0.337 & $-$0.403 & 0.436$^{**}$ & 0.472 & 0.316 \\ 
  & (0.304) & (0.732) & (0.348) & (1.523) & (0.584) & (0.305) & (0.205) & (0.716) & (0.373) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 1,582 & 1,864 & 2,842 & 1,995 & 3,603 & 5,357 & 5,229 & 2,261 & 3,881 \\ 
R$^{2}$ & 0.922 & 0.910 & 0.907 & 0.892 & 0.868 & 0.885 & 0.896 & 0.916 & 0.882 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 12:26:23
\begin{table}[!htbp] \centering 
  \caption{Deciles Employment} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$1.006$^{*}$ & 0.383 & $-$0.452 & 0.041 & $-$0.159 & $-$0.085 & $-$0.726 & $-$0.987$^{*}$ & $-$0.019 \\ 
  & (0.548) & (0.352) & (0.477) & (0.411) & (0.565) & (0.448) & (0.466) & (0.513) & (0.389) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,862 & 4,170 & 3,062 & 3,671 & 2,877 & 3,794 & 2,609 & 1,943 & 2,952 \\ 
R$^{2}$ & 0.892 & 0.882 & 0.923 & 0.903 & 0.906 & 0.885 & 0.903 & 0.915 & 0.906 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/Decile/061_employement_city_thresh.tex
back up before new paper

\begin{document}% Date and time: Sun, Mar 29, 2020 - 11:25:31
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles employment} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.750$^{**}$ & $-$0.604 & $-$0.541$^{*}$ & $-$0.492 & $-$0.254 & $-$0.385$^{***}$ & $-$0.204 & $-$0.185 & $-$0.136 \\ 
  & (0.304) & (0.470) & (0.299) & (0.316) & (0.251) & (0.149) & (0.140) & (0.129) & (0.121) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 1,582 & 3,446 & 6,288 & 8,283 & 11,886 & 17,243 & 22,472 & 24,733 & 28,614 \\ 
R$^{2}$ & 0.922 & 0.889 & 0.875 & 0.861 & 0.847 & 0.851 & 0.854 & 0.852 & 0.848 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

>>>>

\begin{document}% Date and time: Sun, Mar 29, 2020 - 12:27:23
\begin{table}[!htbp] \centering 
  \caption{Cumulative Deciles employment} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{9}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-10} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$1.006$^{*}$ & 0.051 & $-$0.186 & $-$0.116 & $-$0.110 & $-$0.082 & $-$0.121 & $-$0.167 & $-$0.136 \\ 
  & (0.548) & (0.269) & (0.198) & (0.170) & (0.167) & (0.156) & (0.144) & (0.136) & (0.123) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,862 & 8,032 & 11,094 & 14,765 & 17,642 & 21,436 & 24,045 & 25,988 & 28,940 \\ 
R$^{2}$ & 0.892 & 0.867 & 0.868 & 0.862 & 0.860 & 0.854 & 0.851 & 0.852 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank share of [output, capital, employement] of the SOEs \
More specifically, the low deciles means a low presence of SOEs firms in the industries. \
Deciles close to one, however, implies a stronger share of [output, capital, employement] in the \
industries belong to those deciles.
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\%
}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/wrong_cut_bin/011_PRIVATE_city_industry.tex
back up before new paper

\begin{document}% Date and time: Fri, Mar 27, 2020 - 09:33:03
\begin{table}[!htbp] \centering 
  \caption{SOE dominating city-sectors} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{12}{c}{The Dependent variable:} \\ 
\cline{2-13} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12)\\
 \\[-1.8ex]& decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.038 & $-$0.267 & 0.101 & 0.373 & $-$0.166 & $-$0.197 & 0.031 & $-$0.105 & $-$0.027 & $-$0.299 & 0.012 & $-$1.184 \\ 
  & (0.255) & (0.440) & (0.450) & (1.162) & (0.217) & (0.368) & (0.348) & (1.034) & (0.267) & (0.441) & (0.442) & (1.025) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 8,840 & 4,946 & 4,248 & 1,842 & 8,835 & 5,032 & 5,402 & 1,821 & 8,664 & 4,782 & 4,790 & 1,780 \\ 
R$^{2}$ & 0.879 & 0.906 & 0.923 & 0.966 & 0.883 & 0.909 & 0.912 & 0.964 & 0.883 & 0.913 & 0.918 & 0.960 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{12}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{12}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{12}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

>>>>

\begin{document}% Date and time: Fri, Mar 27, 2020 - 09:35:02
\begin{table}[!htbp] \centering 
  \caption{Private dominating city-sectors} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{12}{c}{The Dependent variable:} \\ 
\cline{2-13} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12)\\
 \\[-1.8ex]& decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.202 & $-$0.160 & $-$0.222$^{*}$ & $-$0.155 & $-$0.212 & $-$0.183 & $-$0.199 & $-$0.145 & $-$0.239$^{*}$ & $-$0.148 & $-$0.193 & $-$0.161 \\ 
  & (0.140) & (0.119) & (0.129) & (0.122) & (0.138) & (0.125) & (0.131) & (0.121) & (0.141) & (0.116) & (0.126) & (0.120) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 21,836 & 25,730 & 26,428 & 28,834 & 21,841 & 25,644 & 25,274 & 28,855 & 22,012 & 25,894 & 25,886 & 28,896 \\ 
R$^{2}$ & 0.862 & 0.858 & 0.856 & 0.853 & 0.861 & 0.856 & 0.855 & 0.853 & 0.860 & 0.856 & 0.855 & 0.854 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{12}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{12}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{12}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/wrong_cut_bin/020_SOE_industry.tex
back up before new paper

\begin{document}% Date and time: Fri, Mar 27, 2020 - 09:35:02
\begin{table}[!htbp] \centering 
  \caption{Private dominating city-sectors} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{12}{c}{The Dependent variable:} \\ 
\cline{2-13} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12)\\
 \\[-1.8ex]& decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.202 & $-$0.160 & $-$0.222$^{*}$ & $-$0.155 & $-$0.212 & $-$0.183 & $-$0.199 & $-$0.145 & $-$0.239$^{*}$ & $-$0.148 & $-$0.193 & $-$0.161 \\ 
  & (0.140) & (0.119) & (0.129) & (0.122) & (0.138) & (0.125) & (0.131) & (0.121) & (0.141) & (0.116) & (0.126) & (0.120) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 21,836 & 25,730 & 26,428 & 28,834 & 21,841 & 25,644 & 25,274 & 28,855 & 22,012 & 25,894 & 25,886 & 28,896 \\ 
R$^{2}$ & 0.862 & 0.858 & 0.856 & 0.853 & 0.861 & 0.856 & 0.855 & 0.853 & 0.860 & 0.856 & 0.855 & 0.854 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{12}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{12}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{12}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

>>>>

\begin{document}% Date and time: Fri, Mar 27, 2020 - 09:39:00
\begin{table}[!htbp] \centering 
  \caption{SOE dominating sectors} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{12}{c}{The Dependent variable:} \\ 
\cline{2-13} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12)\\
 \\[-1.8ex]& decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.059 & 0.031 & 0.191 & 0.191 & $-$0.080 & 0.074 & 0.161 & 0.289 & $-$0.081 & $-$0.009 & 0.273 & 0.151 \\ 
  & (0.134) & (0.160) & (0.183) & (0.183) & (0.140) & (0.172) & (0.184) & (0.218) & (0.142) & (0.160) & (0.203) & (0.237) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 24,942 & 18,946 & 10,055 & 10,027 & 24,601 & 17,259 & 11,813 & 9,459 & 24,388 & 18,790 & 11,535 & 8,218 \\ 
R$^{2}$ & 0.852 & 0.859 & 0.869 & 0.868 & 0.852 & 0.858 & 0.868 & 0.868 & 0.851 & 0.857 & 0.861 & 0.872 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{12}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{12}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{12}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/wrong_cut_bin/021_PRIVATE_industry.tex
back up before new paper

\begin{document}% Date and time: Fri, Mar 27, 2020 - 09:39:00
\begin{table}[!htbp] \centering 
  \caption{SOE dominating sectors} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{12}{c}{The Dependent variable:} \\ 
\cline{2-13} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12)\\
 \\[-1.8ex]& decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.059 & 0.031 & 0.191 & 0.191 & $-$0.080 & 0.074 & 0.161 & 0.289 & $-$0.081 & $-$0.009 & 0.273 & 0.151 \\ 
  & (0.134) & (0.160) & (0.183) & (0.183) & (0.140) & (0.172) & (0.184) & (0.218) & (0.142) & (0.160) & (0.203) & (0.237) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 24,942 & 18,946 & 10,055 & 10,027 & 24,601 & 17,259 & 11,813 & 9,459 & 24,388 & 18,790 & 11,535 & 8,218 \\ 
R$^{2}$ & 0.852 & 0.859 & 0.869 & 0.868 & 0.852 & 0.858 & 0.868 & 0.868 & 0.851 & 0.857 & 0.861 & 0.872 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{12}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{12}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{12}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

>>>>

\begin{document}% Date and time: Fri, Mar 27, 2020 - 09:39:54
\begin{table}[!htbp] \centering 
  \caption{Private dominating sectors} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{12}{c}{The Dependent variable:} \\ 
\cline{2-13} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12)\\
 \\[-1.8ex]& decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.787$^{**}$ & $-$0.432$^{**}$ & $-$0.233$^{*}$ & $-$0.233$^{*}$ & $-$0.563 & $-$0.343$^{**}$ & $-$0.306$^{**}$ & $-$0.278$^{**}$ & $-$0.541$^{*}$ & $-$0.254 & $-$0.305$^{**}$ & $-$0.204 \\ 
  & (0.326) & (0.215) & (0.136) & (0.136) & (0.350) & (0.174) & (0.137) & (0.131) & (0.299) & (0.251) & (0.137) & (0.140) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 5,734 & 11,730 & 20,621 & 20,649 & 6,075 & 13,417 & 18,863 & 21,217 & 6,288 & 11,886 & 19,141 & 22,458 \\ 
R$^{2}$ & 0.876 & 0.849 & 0.855 & 0.855 & 0.871 & 0.859 & 0.851 & 0.856 & 0.875 & 0.847 & 0.860 & 0.854 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{12}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{12}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{12}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/wrong_cut_bin/030_SOE_city.tex
back up before new paper

\begin{document}% Date and time: Fri, Mar 27, 2020 - 09:39:54
\begin{table}[!htbp] \centering 
  \caption{Private dominating sectors} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{12}{c}{The Dependent variable:} \\ 
\cline{2-13} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12)\\
 \\[-1.8ex]& decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.787$^{**}$ & $-$0.432$^{**}$ & $-$0.233$^{*}$ & $-$0.233$^{*}$ & $-$0.563 & $-$0.343$^{**}$ & $-$0.306$^{**}$ & $-$0.278$^{**}$ & $-$0.541$^{*}$ & $-$0.254 & $-$0.305$^{**}$ & $-$0.204 \\ 
  & (0.326) & (0.215) & (0.136) & (0.136) & (0.350) & (0.174) & (0.137) & (0.131) & (0.299) & (0.251) & (0.137) & (0.140) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 5,734 & 11,730 & 20,621 & 20,649 & 6,075 & 13,417 & 18,863 & 21,217 & 6,288 & 11,886 & 19,141 & 22,458 \\ 
R$^{2}$ & 0.876 & 0.849 & 0.855 & 0.855 & 0.871 & 0.859 & 0.851 & 0.856 & 0.875 & 0.847 & 0.860 & 0.854 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{12}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{12}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{12}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

>>>>

\begin{document}% Date and time: Fri, Mar 27, 2020 - 09:43:16
\begin{table}[!htbp] \centering 
  \caption{SOE dominating city} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{12}{c}{The Dependent variable:} \\ 
\cline{2-13} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12)\\
 \\[-1.8ex]& decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.187 & $-$0.283 & $-$0.247 & $-$0.068 & $-$0.084 & $-$0.225 & $-$0.205 & $-$0.032 & $-$0.146 & $-$0.266 & $-$0.236 & $-$0.206 \\ 
  & (0.160) & (0.174) & (0.208) & (0.247) & (0.155) & (0.172) & (0.174) & (0.270) & (0.155) & (0.175) & (0.184) & (0.258) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 19,884 & 13,240 & 10,516 & 7,465 & 20,004 & 12,942 & 13,062 & 7,528 & 19,730 & 13,214 & 12,226 & 6,668 \\ 
R$^{2}$ & 0.858 & 0.866 & 0.867 & 0.877 & 0.858 & 0.867 & 0.867 & 0.875 & 0.857 & 0.862 & 0.864 & 0.884 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{12}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{12}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{12}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}
